InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-02-06 paper.tex
Update paper.tex
add initial

Another image generative model is \textbf{midjourney} \cite{midjourney}. This model was created by an identically named and independent research lab. It can synthesize images from textual descriptions. Midjourney tends to generate surrealistic images and is popular among artists. It uses modern deep learning methods to create high-quality images.

\textbf{Imagen} is a text-to-image diffusion model with an unprecedented degree of photorealism and a deep level of language understanding. Imagen builds on the power of large transformer language models in understanding text and hinges on the strength of diffusion models in high-fidelity image generation. \cite{imagen, saharia2022photorealistic}

@@

\section{Conclusion}

>>>>

@@

\section{Conclusion}
Overall we did not find any general fooling technique that can be considered in new AI detectors. We discovered that the detector both for the image and text is highly dependent on the used generator and therefore a processor might reduce the detection rate for some detectors, but on others increase the rate. Our pipeline consisting of creation, process and detection is simple but effective and can be used in further research.
